%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Research Assistant} % Job title
    {NAU SICCS Machine Learning Lab} % Organization
    {\textbf{Flagstaff, Arizona}} % Location
    {\textbf{Oct. 2018 - Present}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working within a diverse lab team to develop Machine Learning algorithms for accurate, scalable, and cost-effective genomic data analysis for cancer diagnosis and prediction using C++ and R.}
        \item {Proved time/space complexity of new change point detection algorithms and implemented necessary data structures for efficient computation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Engineering Intern} % Job title
    {PetSmart} % Organization
    {\textbf{Phoenix, Arizona}} % Location
    {\textbf{May. 2020 - Present}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This internship with PetSmart was an IT Engineering internship that entailed shallow learning concepts in Python. However, the official internship was modified due to COVID-19 concerns. The internship transitioned into a remote Summer Experience where I designed IT systems using Agile methodologies such as Scrum.}
        {}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Branch Chair} % Job title
    {Northern Arizona University IEEE} % Organization
    {\textbf{Flagstaff, Arizona}} % Location
    {\textbf{Oct. 2018 - Oct. 2019}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of officers to hold Computer Science and Electrical Engineering related workshops, events, and hackathons.}
        \item {Improved event attendance by 40\% through tracking of student interests and demographics.}
        \item {Held workshops on C programming to fill in a knowledge gap required for advanced courses such as Operating Systems.}
      \end{cvitems}
    }


\end{cventries}
