\newcommand{\ts}{\textsuperscript}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Research Publication }% Affiliation/role
    {Linear Time Dynamic Programming Algorithm for the Exact Path of Optimal Models}     
    {\textbf{Mar 2020}}%Organization/group
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed and proved a new linear time dynamic programming algorithm for selecting the exact path of optimal changepoint segmentation models from a finite set provided by binary segmentation. \href{https://arxiv.org/abs/2003.02808}{View the publication here.}}
        \item { Observed a \textbf{200\% (x4) speedup} of processing time over previous quadratic time algorithms. Algorithm was developed using C++ and R.}
      \end{cvitems}
    }
    
 \cventry
    {OS development with C} % Affiliation/role
    {Operating System Simulator} % Organization/group
    {\textbf{Apr 2020}}%Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Implemented a C based Operating System Simulator that simulates process selection algorithms, multithreading, concurrent processing with context switching, and memory management. Developed exclusively within a Linux command-line environment.}
        \item {Demonstrated clean coding practices by developing a C codebase with 1000+ lines of code with no memory leaks reported through valgrind.}
      \end{cvitems}
    }
    
    \cventry
    {Android Development with Java} % Affiliation/role
    {Chore Tracker Android App} % Organization/group
    {\textbf{Apr 2020}}%Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created an app that incentivises users to complete household chores. \textbf{The app achieved 1\ts{st} place of 6 competing teams} when presented in a mock investor meeting due to its outstanding user interface design and marketable concept. Developed using Java, SQLite, and AWS.}
      \end{cvitems}
     }
 \cventry
    {Arduino Robotics} % Affiliation/role
    {Line Following Robot} % Organization/group
    {\textbf{Mar 2018}}%Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Formed a team with four other NAU IEEE members to create a C++ based Arduino robot that followed a preset path to completion.}
        \item{\textbf{Placed 2\ts{nd} of 8 teams} in attendance as the bot completed 90\% of the path.}
      \end{cvitems}
     }
\end{cventries}
